\mainmatter

# Notes

Build the book:

```{r eval=F}
bookdown::render_book("index.Rmd", "bookdown::gitbook")
bookdown::render_book("index.Rmd", "bookdown::pdf_book")
bookdown::render_book("index.Rmd", "all") # builds all outputs defined in _output.yml
```
Build a specific chapter only:

```{r eval=F}
bookdown::preview_chapter("chapter.Rmd", "bookdown::gitbook")
```

Auto-update view in browser ([http://127.0.0.1:4321](http://127.0.0.1:4321)) when saving a `.Rmd` file (from [here](https://bookdown.org/yihui/bookdown/serve-the-book.html)). To stop the server, run `servr::daemon_stop("140206388818696")` or restart your R session:

```{r eval=F}
bookdown::serve_book(dir=".", output_dir="_book", preview=TRUE, in_session=TRUE, quiet=FALSE, ...)
```

Cache time consuming code chunks not to run them in every new knit

    `r ''````{r important-computing, cache=T}

Run a script 

    `r ''````{r code=readLines("myscript.R")}

Create bib entries from a package:

```{r eval=F}
knitr::write_bib(c("knitr", "stringr"), "", width = 60)
```

In labels, no `.` signs are allowed. 

Here comes a citet ref @kelley_2018 and here the citep example [@kelley_2018].

## Code-folding button

This button is based on

- https://stackoverflow.com/questions/45360998/code-folding-in-bookdown
- https://github.com/twbs/bootstrap/tree/v3.3.7/js
- https://github.com/rstudio/bookdown/issues/395

